Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-30 MDPI_submission.tex
Commit 2023-11-30 06:14

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X}
\toprule
slope & slope.p & Rsqrd & RsqrdAdj & cor.t & cor.esimate & cor.conf\_int\_1 & cor.conf\_int\_2 & DATA & N & slope.stat\_sig\\
\midrule
0.376 & 0.00000 & 0.008308 & 0.008211 & 9.268 & 0.09115 & 0.07192 & 0.11031 & All skies & 10256 & 100.00\\
0.349 & 0.00000 & 0.006183 & 0.006087 & 7.987 & 0.07864 & 0.05937 & 0.09784 & Clear skies & 10256 & 100.00\\
-0.276 & 0.00026 & 0.002631 & 0.002434 & -3.655 & -0.05129 & -0.07872 & -0.02379 & Cloudy skies & 5067 & 99.97\\
\bottomrule
\end{tabu}
\end{table}

@@

\caption{\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & slope.p & cor.t & cor.esimate & cor.conf\_int\_1 & cor.conf\_int\_2 & Sky condition & Season & slope.stat\_sig\\
\midrule
\cellcolor{gray!6}{0.6860} & \cellcolor{gray!6}{0.001300} & \cellcolor{gray!6}{3.5748458} & \cellcolor{gray!6}{0.5598043} & \cellcolor{gray!6}{0.2499438} & \cellcolor{gray!6}{0.7656559} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{99.9}\\
\cmidrule{1-9}
0.1450 & 0.182000 & 1.3668258 & 0.2460126 & -0.1186724 & 0.5522150 & All skies & Spring & 81.8\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.1200} & \cellcolor{gray!6}{0.106000} & \cellcolor{gray!6}{1.6689762} & \cellcolor{gray!6}{0.3007995} & \cellcolor{gray!6}{-0.0666976} & \cellcolor{gray!6}{0.5964339} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{89.4}\\
\cmidrule{1-9}
0.4310 & 0.006650 & 2.9317564 & 0.4846362 & 0.1506747 & 0.7193136 & All skies & Autumn & 99.3\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.8260} & \cellcolor{gray!6}{0.000259} & \cellcolor{gray!6}{4.1794536} & \cellcolor{gray!6}{0.6198226} & \cellcolor{gray!6}{0.3341758} & \cellcolor{gray!6}{0.8011848} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{100.0}\\
\cmidrule{1-9}
0.0613 & 0.614000 & 0.5095289 & 0.0941964 & -0.2691265 & 0.4340490 & Clear skies & Spring & 38.6\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.0307} & \cellcolor{gray!6}{0.741000} & \cellcolor{gray!6}{-0.3343454} & \cellcolor{gray!6}{-0.0630596} & \cellcolor{gray!6}{-0.4139251} & \cellcolor{gray!6}{0.3041187} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{25.9}\\
\cmidrule{1-9}
0.3670 & 0.028300 & 2.3126418 & 0.4004713 & 0.0469803 & 0.6648218 & Clear skies & Autumn & 97.2\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.8820} & \cellcolor{gray!6}{0.011100} & \cellcolor{gray!6}{-2.7197359} & \cellcolor{gray!6}{-0.4571342} & \cellcolor{gray!6}{-0.7018198} & \cellcolor{gray!6}{-0.1159631} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{98.9}\\
\cmidrule{1-9}
-0.0991 & 0.628000 & -0.4892643 & -0.0904814 & -0.4310031 & 0.2725985 & Cloudy skies & Spring & 37.2\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.0444} & \cellcolor{gray!6}{0.785000} & \cellcolor{gray!6}{0.2750824} & \cellcolor{gray!6}{0.0519156} & \cellcolor{gray!6}{-0.3142309} & \cellcolor{gray!6}{0.4046170} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{21.5}\\
\cmidrule{1-9}
-0.4000 & 0.105000 & -1.6769099 & -0.3020992 & -0.5973542 & 0.0652743 & Cloudy skies & Autumn & 89.5\\
\bottomrule
\end{tabu}
\end{table}

>>>>

\begin{verbatim}
Warning in set(x, j = name, value = value): Column 'cor.null_value' does not
exist to remove
\end{verbatim}

\begin{verbatim}
Warning in set(x, j = name, value = value): Column 'cor.alternative' does not
exist to remove
\end{verbatim}

\begin{verbatim}
Warning in set(x, j = name, value = value): Column 'cor.method' does not exist
to remove
\end{verbatim}

\begin{verbatim}
Warning in set(x, j = name, value = value): Column 'cor.data_name' does not
exist to remove
\end{verbatim}

\begin{verbatim}
Warning in set(x, j = name, value = value): Column 'cor.p' does not exist to
remove
\end{verbatim}

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
slope & slope.p & Rsqrd & RsqrdAdj & cor.t & cor.esimate & DATA & N & slope.stat\_sig\\
\midrule
0.376 & 0.00000 & 0.008308 & 0.008211 & 9.268 & 0.09115 & All skies & 10256 & 100.00\\
0.349 & 0.00000 & 0.006183 & 0.006087 & 7.987 & 0.07864 & Clear skies & 10256 & 100.00\\
-0.276 & 0.00026 & 0.002631 & 0.002434 & -3.655 & -0.05129 & Cloudy skies & 5067 & 99.97\\
\bottomrule
\end{tabu}
\end{table}

@@

\caption{\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & slope.p & Rsqrd & RsqrdAdj & cor.t & cor.esimate & Sky condition & Season & slope.stat\_sig\\
\midrule
\cellcolor{gray!6}{0.6860} & \cellcolor{gray!6}{0.001300} & \cellcolor{gray!6}{0.3133809} & \cellcolor{gray!6}{0.2888588} & \cellcolor{gray!6}{3.5748458} & \cellcolor{gray!6}{0.5598043} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{99.9}\\
\cmidrule{1-9}
0.1450 & 0.182000 & 0.0605222 & 0.0281264 & 1.3668258 & 0.2460126 & All skies & Spring & 81.8\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.1200} & \cellcolor{gray!6}{0.106000} & \cellcolor{gray!6}{0.0904804} & \cellcolor{gray!6}{0.0579975} & \cellcolor{gray!6}{1.6689762} & \cellcolor{gray!6}{0.3007995} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{89.4}\\
\cmidrule{1-9}
0.4310 & 0.006650 & 0.2348722 & 0.2075462 & 2.9317564 & 0.4846362 & All skies & Autumn & 99.3\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.8260} & \cellcolor{gray!6}{0.000259} & \cellcolor{gray!6}{0.3841800} & \cellcolor{gray!6}{0.3621864} & \cellcolor{gray!6}{4.1794536} & \cellcolor{gray!6}{0.6198226} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{100.0}\\
\cmidrule{1-9}
0.0613 & 0.614000 & 0.0088730 & -0.0253038 & 0.5095289 & 0.0941964 & Clear skies & Spring & 38.6\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.0307} & \cellcolor{gray!6}{0.741000} & \cellcolor{gray!6}{0.0039765} & \cellcolor{gray!6}{-0.0315958} & \cellcolor{gray!6}{-0.3343454} & \cellcolor{gray!6}{-0.0630596} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{25.9}\\
\cmidrule{1-9}
0.3670 & 0.028300 & 0.1603773 & 0.1303908 & 2.3126418 & 0.4004713 & Clear skies & Autumn & 97.2\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.8820} & \cellcolor{gray!6}{0.011100} & \cellcolor{gray!6}{0.2089717} & \cellcolor{gray!6}{0.1807207} & \cellcolor{gray!6}{-2.7197359} & \cellcolor{gray!6}{-0.4571342} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{98.9}\\
\cmidrule{1-9}
-0.0991 & 0.628000 & 0.0081869 & -0.0260136 & -0.4892643 & -0.0904814 & Cloudy skies & Spring & 37.2\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.0444} & \cellcolor{gray!6}{0.785000} & \cellcolor{gray!6}{0.0026952} & \cellcolor{gray!6}{-0.0329228} & \cellcolor{gray!6}{0.2750824} & \cellcolor{gray!6}{0.0519156} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{21.5}\\
\cmidrule{1-9}
-0.4000 & 0.105000 & 0.0912639 & 0.0588091 & -1.6769099 & -0.3020992 & Cloudy skies & Autumn & 89.5\\
\bottomrule
\end{tabu}
\end{table}
